### 2018-10-14 papers/journal/experiments.tex
Improved Experimentation and Previous work

We have developed three different tools (satVTS, smtVTS, synthVTS) for implementation of proposed encodings. All the experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.

>>>>

We have developed three different tools (\sattool, \smttool, \ourtool) for implementation of proposed encodings. {\sattool} is based on the architecture of a Bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem. {\smttool} is based on the SMT solver Z3 and uses the efficient encoding of finding a least fixed point to solve reachability problem. The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS. It is based on the QBF encoding and uses {\depqbf} solver to solve the generated QBF. All the experiments were done on a machine with Intel(R) Core(TM) i3-4030U CPU @ 1.90GHz processor and 4GB RAM with 30 min (1800 sec) timeout.

### 2018-10-14 papers/journal/related.tex
Improved Experimentation and Previous work

SAT and SMT solvers are a perfect fit for solving combinatorial problems due to their exhaustive nature of searching. 
%
Improvement in SAT and SMT solvers in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules with possible exhaustive search and hence can be reduced to solving a SAT/SMT question. 
%
Modeling and understanding the gene regulatory networks (GNR)~\cite{guerra2012reasoning,chin2008biographe}, modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis} is one such example. 
%
We have extended the application of SAT and SMT solvers to the most comple Biological transport network (VTS)~\cite{mani2016stacking,shukla}.

>>>>

\begin{table}[!ht]
	%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
	\centering
	\begin{tabular}{|c|c|}
		\hline 
		\textbf{N} & \textbf{Total Number of graphs} \\ \hline
		1.         & 0                               \\ \hline
		2.         & 0                               \\ \hline
		3.         & 0                               \\ \hline
		4.         & 1                               \\ \hline
		5.         & 2                               \\ \hline
		6.         & 15                              \\ \hline
		7.         & 121                             \\ \hline
		8.         & 2159                            \\ \hline
		9.         & 68715                           \\ \hline
		10.        & 3952378                         \\ \hline
	\end{tabular}
	\label{tab-graphs}
     \caption{Number of simple 3-edge-connected unlabeled N-node graphs.}
	%\end{adjustwidth}
\end{table}

The analysis of vesicle traffic systems is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
For example, we might want to check some conjecture of interest for all 3-connected graphs and
all possible variations of SNARE regulation rules. 
%
The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab-graphs} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
%

Previous analyses of VTS have mostly been based on sampling approach~\cite{mani2016wine, mani2016stacking}. 
%
In these analyses, vesicle traffic is
modeled as a dynamical system. 
%
The traffic rule specifies how the system transitions from one
time point to the next. 
%
Given a traffic rule and an initial condition, the system is evolved over time until a steady state is reached. By studying a large sample of randomly generated traffic
rules, such analyses can make statistical claims about vesicle traffic.
%
Hence making precise general prediction about the properties of vesicle traffic networks over all possible traffic rules, not just for a sampled subset is not possible.
%
SAT and SMT solvers are a perfect fit for this situation, solving combinatorial problems with their exhaustive nature of searching. 
%
These tools check a specified logical property
on every possible state of a model constructed using variables ranging over Boolean or any
finite discrete type.

Improvement in SAT and SMT solvers in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules with possible exhaustive search and hence can be reduced to solving a SAT/SMT question. 
%
Modeling and understanding the gene regulatory networks (GNR)~\cite{guerra2012reasoning,chin2008biographe}, modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis} is one such example. 
%
We have extended the application of SAT and SMT solvers to the most comple Biological transport network (VTS)~\cite{mani2016stacking,shukla}.

### 2018-10-14 papers/journal/result-table.tex
Improved Experimentation and Previous work

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\def\arraystretch{1.6}
\caption{
{\bf SNARE regulation and graph connectedness.}}
\begin{tabular}{|c|l|l|c|}
\hline
\bf{Sr.No} & \multicolumn{1}{c|}{\bf{Regulation on node}} & \bf{Regulation on edge} & \bf{Connectedness}\\ \thickhline
1. & Boolean function & Boolean function & N = 2C S = 3C \\ \hline
2. & None & Boolean function & N \& S = 3C\\ \hline
3. & Boolean function & SNARE-SNARE inhibition & N \& S = 4C\\ \hline
4. & None & SNARE-SNARE inhibition & No graphs found\\ \hline
5. & Boolean function & None & No graphs found\\ \hline
6. &  None & None & No graphs found\\ \hline

>>>>

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\def\arraystretch{1.6}
\caption{
{\bf SNARE regulation and graph connectedness.}}
\begin{tabular}{|c|c|c|c|c|}
\hline
\bf{Sr.No} & \multicolumn{1}{c|}{\bf{Regulation on node}} & \bf{Regulation on edge} & \bf{Connectedness} & \bf{Timing} \\  \thickhline
1. & Boolean function & Boolean function & 2C & \\ \hline
2. & None & Boolean function & 3C & \\ \hline
3. & Boolean function & SNARE-SNARE inhibition & 4C & \\ \hline
4. & None & SNARE-SNARE inhibition & No graphs found & \\ \hline
5. & Boolean function & None & No graphs found & \\ \hline
6. &  None & None & No graphs found & \\ \hline
